\ourTitle

### 2022-06-08 paper/manuscript.tex
JPC: Done with edit pass. Now to submit.

The even process, as in all other cases seen thus far, has two dominant
prediction clusters. These correspond to the predictive states that result
from seeing an even-sized block of $1$s (or, equivalently, no $1$s) and that
result from seeing an odd-sized block of $1$s. The lone cluster in the middle
corrresponds to a transient state induced by seeing all $1$s and then a $0$.
The latter then synchronizes to right cluster.

@@

STOPPED

@@

%% The acknowledgments section is defined using the "acks" environment % (and
%NOT an unnumbered section). This ensures the proper % identification of the
%section in the article metadata, and the % consistent spelling of the heading.
\section*{Acknowledgements}
We thank Nicolas Brodu, Adam Rupe, Alex Jurgens, David Gier, and Mikhael
Semaan. JPC acknowledges the kind hospitality of the Telluride Science
Research Center, Santa Fe Institute, Institute for Advanced Study at the
University of Amsterdam, and California Institute of Technology for their
hospitality during visits. This material is based upon work supported by, or
in part by, Templeton World Charity Foundation Diverse Intelligences grants TWCF0440 and TWCF0570 and Foundational Questions Institute and Fetzer Franklin Fund grant number FQXI-RFP-CPW-2007 and grants W911NF-18-1-0028 and
W911NF-21-1-0048 from the U.S. Army Research Laboratory and the U.S. Army
Research Office.

\section*{Reproducibility statement}
For the purposes of reproducibility, we provide a 
GitHub repository \cite{repo} containing
the code necessary to generate this manuscript and its figures, including a
notebook for generating the data used for the examples and for building both
static and interactive figures for further exploration.
%%
%% The next two lines define the bibliography style to be used, and % the
%bibliography file.
\bibliography{ref}

>>>>

The even process, as in all other cases seen thus far, has two dominant
prediction clusters. These correspond to the predictive states that result
from seeing an even-sized block of $1$s (or, equivalently, no $1$s) and that
result from seeing an odd-sized block of $1$s. The lone cluster in the middle
corresponds to a transient state induced by seeing all $1$s and then a $0$.
The latter then synchronizes to right cluster.

@@

@@

%% The acknowledgments section is defined using the "acks" environment % (and
%NOT an unnumbered section). This ensures the proper % identification of the
%section in the article metadata, and the % consistent spelling of the heading.
\vspace{-0.2in}
\section*{Acknowledgments}
\vspace{-0.2in}
We thank Nicolas Brodu, Adam Rupe, Alex Jurgens, David Gier, and Mikhael
Semaan. JPC acknowledges the kind hospitality of the Telluride Science
Research Center, Santa Fe Institute, Institute for Advanced Study at the
University of Amsterdam, and California Institute of Technology for their
hospitality during visits. This material is based upon work supported by, or
in part by, Templeton World Charity Foundation Diverse Intelligences grants TWCF0440 and TWCF0570 and Foundational Questions Institute and Fetzer Franklin Fund grant number FQXI-RFP-CPW-2007 and grants W911NF-18-1-0028 and
W911NF-21-1-0048 from the U.S. Army Research Laboratory and the U.S. Army
Research Office.

\vspace{-0.2in}
\section*{Reproducibility statement}
\vspace{-0.2in}
For the purposes of reproducibility, we provide a 
GitHub repository \cite{repo} containing
the code necessary to generate this manuscript and its figures, including a
notebook for generating the data used for the examples and for building both
static and interactive figures for further exploration.
%%
%% The next two lines define the bibliography style to be used, and % the
%bibliography file.

\bibliography{ref}
